Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-14 paper/structureScene.tex
remove ja's comment on sum of probabilities
minor changes in biographies

Conversely, a late integration scheme relies on probabilistic assignments $\mathbb{P}\left[y \,\vert\, \mathbf{S}\boldsymbol{x}(t,\gamma) \right]$ over short-term windows of length $T$ obtained from some supervised model, such as a classifier. These are subsequently aggregated to produce a final decision
\begin{equation}
\hat{y} = \arg \max_{y} \rho\Big(\big\{ \mathbb{P}\left[y \,\vert\, \mathbf{S}\boldsymbol{x}(t,\gamma) \right] \big\}_{t} \Big)\mbox{,}
\end{equation}
where $\hat{y}$ is the estimated class label and $\rho$ is a reduction function, such as sum, product, or majority vote \cite{Kittler1998}. \ja{Do we really sum probabilities? Seems like a strange thing to do.}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{gfx/lostanlen}}]{Vincent Lostanlen} was born in 1992. He received his M.S. degree in acoustics, signal processing, and musical informatics (ATIAM) from the Universit\'{e} Pierre et Marie Curie and the Ircam in Paris, France. Since 2013, he is a PhD student at ENS in Paris.
\end{IEEEbiography}

@@

\begin{IEEEbiography}[{\includegraphics[width=1.25in,height=1.25in,clip,keepaspectratio]{gfx/lagrange}}]{Mathieu Lagrange} is a CNRS research scientist at IRCCyN, a French laboratory dedicated to cybernetics. He obtained his PhD in computer science at the University of Bordeaux in 2004, and visited several institutions in Canada (University of Victoria, McGill University) and in France (Orange Labs, Telecom ParisTech, Ircam). His research focuses on machine listening algorithms applied to the analysis of musical and environmental audio.
\end{IEEEbiography}

>>>>

Conversely, a late integration scheme relies on probabilistic assignments $\mathbb{P}\left[y \,\vert\, \mathbf{S}\boldsymbol{x}(t,\gamma) \right]$ over short-term windows of length $T$ obtained from some supervised model, such as a classifier. These are subsequently aggregated to produce a final decision
\begin{equation}
\hat{y} = \arg \max_{y} \rho\Big(\big\{ \mathbb{P}\left[y \,\vert\, \mathbf{S}\boldsymbol{x}(t,\gamma) \right] \big\}_{t} \Big)\mbox{,}
\end{equation}
where $\hat{y}$ is the estimated class label and $\rho$ is a reduction function, such as sum, product, or majority vote \cite{Kittler1998}.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{gfx/lostanlen}}]{Vincent Lostanlen} was born in 1992. He received his M.S. degree in acoustics, signal processing, and musical informatics (ATIAM) from the Universit\'{e} Pierre et Marie Curie and the Ircam in Paris, France, in 2013. Since 2013, he is a PhD student at ENS in Paris.
\end{IEEEbiography}

@@

\begin{IEEEbiography}[{\includegraphics[width=1.25in,height=1.25in,clip,keepaspectratio]{gfx/lagrange}}]{Mathieu Lagrange} is a CNRS research scientist at IRCCyN, a French laboratory dedicated to cybernetics. He obtained his PhD in computer science at the University of Bordeaux in 2004, and visited several institutions in Canada (University of Victoria, McGill University) and in France (Orange Labs, TELECOM ParisTech, Ircam). His research focuses on machine listening algorithms applied to the analysis of musical and environmental audio.
\end{IEEEbiography}
